Recent Advances in Networking

### 2013-07-26 Compiled/intro/intro.tex
fix
fixes
clickable references for chapters 1 and 2

@@

We wish to thank all there authors for providing such high quality chapters. We are also grateful to the reviewers and the editorial board for spending many hours on each chapter to ensure a coherent level amongst all the chapters. We hope you enjoy reading this eBook and find it a useful resource.

Hamed Haddadi, Olivier Bonaventure

August 2013

>>>>

\pagestyle{empty}

{\Huge \textbf{Introduction}}

\vspace{1in}

@@

We wish to thank all there authors for providing such high quality chapters. We are also grateful to the reviewers and the editorial board for spending many hours on each chapter to ensure a coherent level amongst all the chapters. We hope you enjoy reading this eBook and find it a useful resource.\\

Hamed Haddadi, Olivier Bonaventure \\

\begin{figure}
\begin{center}
\includegraphics[width=3cm]{intro/sigcomm-logo-new}
%\caption{\label{kmeans} {ACM SIGCOMM}}\vspace{-3mm}
\end{center}
\end{figure}
%August 2013 \\
\vspace{1in}
Hamed Haddadi, Olivier Bonaventure, ``Recent Advances in Networking", Volume 1, ACM SIGCOMM eBook, August 2013.
